### 2013-12-30 Paper_Markdown.Rmd

```{r Fig1SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}
map <- map_data('world')

@@

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE}

@@

model.out <- data.frame(site   = rep(rep(climate[,1], ncol(wa.res$bias)),5),
                        preds  = c(as.vector(mat.res$mean_prediction),
                                   as.vector(wa.res$mean_prediction),
                                   as.vector(wapls.res$mean_prediction),
                                   as.vector(rfor.res$mean_prediction),
                                   as.vector(brt.res$mean_prediction)),
                        bias   = c(as.vector(mat.res$bias),
                                   as.vector(wa.res$bias),
                                   as.vector(wapls.res$bias),
                                   as.vector(rfor.res$bias),
                                   as.vector(brt.res$bias)),
                        variance = c(as.vector(mat.res$variance),
                                   as.vector(wa.res$variance),
                                   as.vector(wapls.res$variance),
                                   as.vector(rfor.res$variance),
                                   as.vector(brt.res$variance)),
                        dissim = rep(rep(vals, each=nrow(wa.res$bias)),5),
                        model  = rep(c('MAT', 'WA', 'WAPLS', 'rFor', 'BRT'), each = length(wa.res$bias)),
                        init = rep(climate[,10], ncol(wa.res$bias), 5))

#  This kills ~ 300,000 rows right now because of gaps in rfor.res and brt.res.
model.out <- model.out[!rowSums(is.na(model.out)) > 0,]
#  This is a temporary fix, 
samp.set <- sapply(c('MAT', 'WA', 'WAPLS', 'rFor', 'BRT'), function(x){
  set.len <- sum(model.out$model == x)
  if( set.len > 5000) set.len <- 5000
  sample(which(model.out$model == x), set.len)
})

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value') +
  ylim(0, 40)

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(bias), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt(expand = c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bias (RMSEP)')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(variance), group = site, color = init)) +
  geom_path(alpha = 0.05) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bootstrap Variance')

>>>>

```{r Fig1SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}

map <- map_data('world')

@@

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6}

@@

init.color <- colorRampPalette(c('#F08080', '#68d64f', '#4169E1'))
clim.colors <- seq(0, 31, length.out = 300)
init.set <- init.color(300)[findInterval(x = climate[,10], vec=clim.colors)]

model.out <- data.frame(site   = rep(rep(climate[,1], ncol(wa.res$bias)),5),
                        preds  = c(as.vector(mat.res$mean_prediction),
                                   as.vector(wa.res$mean_prediction),
                                   as.vector(wapls.res$mean_prediction),
                                   as.vector(rfor.res$mean_prediction),
                                   as.vector(brt.res$mean_prediction)),
                        bias   = c(as.vector(mat.res$bias),
                                   as.vector(wa.res$bias),
                                   as.vector(wapls.res$bias),
                                   as.vector(rfor.res$bias),
                                   as.vector(brt.res$bias)),
                        variance = c(as.vector(mat.res$variance),
                                   as.vector(wa.res$variance),
                                   as.vector(wapls.res$variance),
                                   as.vector(rfor.res$variance),
                                   as.vector(brt.res$variance)),
                        dissim = rep(rep(vals, each=nrow(wa.res$bias)),5),
                        model  = rep(c('MAT', 'WA', 'WAPLS', 'rFor', 'BRT'), each = length(wa.res$bias)),
                        init = rep(rep(climate[,10], 101), 5))

#  This kills ~ 300,000 rows right now because of gaps in rfor.res and brt.res.
model.out <- model.out[!rowSums(is.na(model.out)) > 0,]

#  This is a temporary fix, 
sample.model <- function(x){
  #  How many samples exist for the model?
  set.len <- sum(model.out$model == x)
  if( set.len > 5000) set.len <- 5000

  set <- sample(which(model.out$model == x), set.len)
  start.end <- which(model.out$model == x & 
                       (model.out$dissim %in% c(0, 0.5, 1)))

  unique(c(set, start.end))

}

samp.set <- sapply(c('MAT', 'WA', 'WAPLS', 'rFor', 'BRT'), sample.model)

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), breaks = c(0.5, 1)) +
  scale_y_continuous(expand=c(0,0), limits=c(0, 40)) +
  scale_color_continuous(low = 'blue', high='pink', trans='sqrt') +
  theme(legend.position = 'none',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  annotate("segment", x=0.48, 
           xend = 0.48, y = 0, yend = 100, size=1, linetype='dashed') +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(bias), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), breaks = c(0.5, 1)) +
  scale_y_sqrt(expand=c(0,0)) +
  scale_color_continuous(low = 'blue', high='pink', trans='sqrt') +
  theme(legend.position = 'none',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bias (RMSEP)')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(variance), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), breaks = c(0.5, 1)) +
  scale_y_sqrt(expand=c(0,0)) +
  scale_color_continuous(low = 'blue', high='pink', trans='sqrt') +
  theme(legend.position = 'none',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bootstrap Variance')
